Individual ABC reject Fits

### 2024-02-15 Model/abc_reject.qmd
progress on model result visuals

```{r}
pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
               stringr,future,furrr, knitr, reactable, flextable,ggstance, htmltools)
conflict_prefer_all("dplyr", quiet = TRUE)
options(scipen = 999)
walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
ds <- readRDS(here::here("data/e1_md_11-06-23.rds"))  |> as.data.table()
test <- readRDS(here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test") 
testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)

@@

ind_fits <- map(list.files(here(paste0('data/abc_reject/'),file_name),full.names=TRUE), readRDS)
# ind_fits <- map(list.files(here('data/abc_reject/n_iter_2000_ntry_10_2918'),full.names=TRUE), readRDS)
ind_fits_df <- ind_fits |> map(~list(dat=.x[[1]], Model = .x[["Model"]], Fit_Method=.x[["Fit_Method"]]))
ind_fits_df <- ind_fits_df |> map(~rbindlist(.x$dat) |> mutate(Model = .x$Model, Fit_Method = .x$Fit_Method)) |> rbindlist() 
avg_samples <- ind_fits_df |> group_by(id,condit,Model,Fit_Method) |> 
  summarise(inc=max(inc_count),iter_sum=sum(iter_count))
mean(avg_samples$iter_sum)
mean(avg_samples$iter_sum)
min(avg_samples$iter_sum)
max(avg_samples$iter_sum)
sum(avg_samples$iter_sum)
sum(avg_samples$iter_sum)
avg_samples |> group_by(Model,Fit_Method) |> summarise(mean(inc),mean(iter_sum))

@@

@@

pd_train_l <- pd_train_l |> mutate(dist=abs(x-val))

@@

theta_map <- post_dat_avg |> group_by(condit,Model,Fit_Method) |> summarize(c=median(c),lr=median(lr))

map <- simulation_function(sbj_data <- ds |> theta_map$c[1], , params$lr, input_layer = input_layer, 
                                    output_layer = output_layer, return_dat = return_dat)

@@

@@

## More Comparisons
```{r fig.width=11, fig.height=12}

best_id_x <- post_dat |> group_by(id,condit,Model,Fit_Method,x) |>
  mutate(e2=abs(y-pred)) |>
  summarise(y=mean(y), pred=mean(pred), mean_error=mean(e2)) |>
  group_by(id,condit,Fit_Method,x) |> mutate(best=ifelse(mean_error==min(mean_error),1,0)) |>
  group_by(id,condit,Fit_Method,Model) |> mutate(n_best=sum(best))

best_id <- best_id_x |> group_by(id,condit,Fit_Method,Model) |>
  summarise(mean_error=mean(mean_error), n_best=first(n_best))

@@

error_difference <- best_id %>%
  select(id, condit, Model,Fit_Method, mean_error) %>%
  pivot_wider(names_from = Model, values_from = mean_error) %>%
  mutate(Error_difference = (ALM - EXAM))

@@

full_comparison |> round_tibble(1) |> reactable(filterable=T,defaultPageSize=15)

@@

>>>>

```{r}
pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
               stringr,future,furrr, knitr, reactable, flextable,ggstance, htmltools)
conflict_prefer_all("dplyr", quiet = TRUE)
options(scipen = 999)
walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
ds <- readRDS(here::here("data/e1_md_11-06-23.rds"))  |> as.data.table()

fd <- readRDS(here("data/e1_08-21-23.rds"))
test <- fd |> filter(expMode2 == "Test") 
testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
nbins=3
trainAvg <- fd |> filter(expMode2 == "Train") |> group_by(id) |> 
  mutate(tr=trial,x=vb,Block=case_when(expMode2=="Train" ~ cut(tr,breaks=seq(1,max(tr), length.out=nbins+1),include.lowest=TRUE,labels=FALSE),
                                         expMode2=="Test" ~ 4)) |> 
  group_by(id,condit,vb,x,Block) |> 
  summarise(dist=mean(dist),y=mean(vx))

# df with trial count columns for each level of expMode, for each id
id_n <- ds |> group_by(id,condit) |> summarise(nTest=n_distinct(tr[expMode2=="Test"]),
                                        nTrain=n_distinct(tr[expMode2=="Train"])) |>
  mutate(nTotal=nTest+nTrain)

testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)

@@

ind_fits <- map(list.files(here(paste0('data/abc_reject/'),file_name),full.names=TRUE), readRDS)
# ind_fits <- map(list.files(here('data/abc_reject/n_iter_2000_ntry_10_2918'),full.names=TRUE), readRDS)
ind_fits_df <- ind_fits |> map(~list(dat=.x[[1]], Model = .x[["Model"]], Fit_Method=.x[["Fit_Method"]]))
ind_fits_df <- ind_fits_df |> map(~rbindlist(.x$dat) |> mutate(Model = .x$Model, Fit_Method = .x$Fit_Method)) |> rbindlist()

avg_samples <- ind_fits_df |> group_by(id,condit,Model,Fit_Method) |> 
  summarise(inc=max(inc_count),iter_sum=sum(iter_count))
mean(avg_samples$iter_sum)
mean(avg_samples$iter_sum)
min(avg_samples$iter_sum)
max(avg_samples$iter_sum)
sum(avg_samples$iter_sum)
sum(avg_samples$iter_sum)
avg_samples |> group_by(Model,Fit_Method) |> summarise(mean(inc),mean(iter_sum))

@@

post_dat_avg2 <- post_dat_avg |>
  group_by(id, condit, Model, Fit_Method, c, lr, rank) |> 
  summarise(y = mean(y), pred = mean(pred), error = y - pred) |> as.data.table() |> arrange(rank)

map_id <- post_dat |> group_by(id, condit, Model, Fit_Method) |> 
  filter(rank==1) |> slice_head(n=1) |> select(id,condit,Fit_Method,Model,c,lr,mean_error,rank) |>
  left_join(id_n,by=(c("id","condit")))

# compute BIC for each row of map_id; p=2 for c and lr
map_id <- map_id |> mutate(n = fifelse(Fit_Method == "Test", nTest, fifelse(Fit_Method == "Train", nTrain, nTotal)),BIC = -2 * log(mean_error) + log(n)*2)

bic_id <- map_id %>%
  group_by(id, Fit_Method) %>%
  arrange(Model) %>%
  summarize(BIC_diff = diff(BIC),
            .groups = 'drop') %>%
  left_join(map_id, by = c("id", "Fit_Method")) %>%
  select(id, Fit_Method, Model, BIC, BIC_diff)

@@

pd_train_l <- pd_train_l |>
  mutate(dist = case_when(
    val >= x & val <= x + 200 ~ 0,                 
    val < x ~ abs(x - val),                       
    val > x + 200 ~ abs(val - (x + 200)),           
    TRUE ~ NA_real_                                 
  ))
plan(sequential)

@@

# theta_map <- post_dat_avg |> group_by(condit,Model,Fit_Method) |> summarize(c=median(c),lr=median(lr))
# 
# map <- simulation_function(sbj_data <- ds |> theta_map$c[1], , params$lr, input_layer = input_layer, 
#                                     output_layer = output_layer, return_dat = return_dat)

@@

post_dist <- post_dat_avg %>%
  group_by(id, condit, Model, Fit_Method, rank) %>%
  slice_head(n = 1) %>%
  ungroup() %>% # Make sure to remove the grouping by rank before the next group_by
  group_by(id, condit, Model, Fit_Method) %>%
  summarize(across(c:lr, list(mean = mean, sd = sd, se = ~sd(.)/sqrt(n()))), .groups = 'keep')

post_dist |> 
  group_by(condit, Model, Fit_Method) %>%
  mutate(across(c_mean, list(gmean = mean, gsd = sd, gse = ~sd(.)/sqrt(n()))), .groups = 'keep') |>
  filter(c_mean<(c_mean_gmean+(.5*c_mean_gse))) |>
  ggplot(aes(y=id, x = c_mean)) + 
  stat_pointinterval() + 
  ggh4x::facet_nested_wrap(Fit_Method~condit~Model,scales="free")

post_dist |> 
  group_by(condit, Model, Fit_Method) %>%
  mutate(across(c_mean, list(gmean = median, gsd = sd, gse = ~sd(.)/sqrt(n()))), .groups = 'keep') |>
  filter(c_mean<(c_mean_gmean+(.5*c_mean_gse))) |>
  ggplot(aes( x = c_mean,fill=condit)) + geom_density() +
  ggh4x::facet_nested_wrap(Fit_Method~Model,scales="free")

post_dist |> 
  group_by(condit, Model, Fit_Method) %>%
  mutate(across(c_mean, list(gmean = median, gsd = sd, gse = ~sd(.)/sqrt(n()))), .groups = 'keep') |>
  filter(c_mean<(c_mean_gmean+(.5*c_mean_gse))) |>
  ggplot(aes( x = log(c_mean),fill=condit)) + geom_density() +
  ggh4x::facet_nested_wrap(Fit_Method~Model,scales="free")

 post_dat_avg %>%
    group_by(id, condit, Model, Fit_Method, rank) %>%
    slice_head(n = 1) |>
    ggplot(aes( x = log(c),fill=condit)) + geom_density() +
    ggh4x::facet_nested_wrap(Fit_Method~Model,scales="free")

 post_dat_avg %>%
    group_by(id, condit, Model, Fit_Method, rank) %>%
    slice_head(n = 1) |>
    ggplot(aes(y=Fit_Method, x = log(c),col=condit)) + stat_pointinterval(position=position_dodge(.2)) +
    ggh4x::facet_nested_wrap(~Model,scales="free")

 post_dat_avg %>%
    group_by(id, condit, Model, Fit_Method, rank) %>%
    slice_head(n = 1) |>
    ggplot(aes(y=Fit_Method, x = lr,col=condit)) + stat_pointinterval(position=position_dodge(.2)) +
    ggh4x::facet_nested_wrap(~Model,scales="free")

# post_dat_avg %>%
#     group_by(id, condit, Model, Fit_Method, rank) %>%
#     slice_head(n = 1) |>
#     ggplot(aes(y=Fit_Method, x = (lr),fill=condit)) + 
#     stat_halfeye(position=position_dodge(.2)) +
#     ggh4x::facet_nested_wrap(~Model,scales="free")   
#

@@

## More Comparisons

```{r fig.width=11, fig.height=12}
best_id_x <- post_dat |> group_by(id,condit,Model,Fit_Method,x) |>
  mutate(e2=(y-pred)) |>
  summarise(y=mean(y), pred=mean(pred), mean_error=mean(e2),abs_me=abs(mean_error)) |>
  group_by(id,condit,Fit_Method,x) |> mutate(best=ifelse(mean_error==min(mean_error),1,0)) |>
  group_by(id,condit,Fit_Method,Model) |> mutate(n_best=sum(best))

best_id <- best_id_x |> group_by(id,condit,Fit_Method,Model) |>
  summarise(mean_error=mean(mean_error), n_best=first(n_best),abs_me=mean(abs(mean_error)))

@@

error_difference <- best_id %>%
  select(id, condit, Model,Fit_Method, mean_error,abs_me) %>%
  pivot_wider(names_from = Model, values_from = c(abs_me,mean_error)) %>%
  mutate(Error_difference = (mean_error_ALM - mean_error_EXAM), abs_error_dif = (abs_me_ALM - abs_me_EXAM))

@@

best_id |> filter(Fit_Method=="Test_Train") |> 
  arrange(mean_error) |>
  ungroup() |>
  mutate(id = reorder(id, mean_error)) %>%
  ggplot(aes(y=id,x=mean_error,fill=Model))+
  geom_col()+
  ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")

best_id |> filter(Fit_Method=="Test_Train") |> 
  ungroup() |>
  mutate(id = reorder(id, abs_me)) %>%
  ggplot(aes(y=id,x=abs_me,fill=Model))+
  geom_col()+
  ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")

full_comparison |> filter(Fit_Method=="Test_Train") |> 
  ungroup() |>
  mutate(id = reorder(id, abs_error_dif)) %>%
  ggplot(aes(y=id,x=abs_error_dif))+
  geom_col()+
  ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")

full_comparison |> filter(Fit_Method=="Test_Train") |> 
  ungroup() |>
  mutate(id = reorder(id, Error_difference)) %>%
  ggplot(aes(y=id,x=Error_difference))+
  geom_col()+
  ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")

d <- testAvg |> left_join(full_comparison, by=c("id","condit")) |> filter(Fit_Method=="Test_Train")

d |> 
  group_by(condit,Fit_Method,Best_Model) |> 
  mutate(nGrp2=n()) |>
  filter(abs(Error_difference)>15) |> 
  ggplot(aes(x=vb,y=dist,fill=condit)) + 
  stat_bar + facet_wrap(Fit_Method~Best_Model,ncol=2)

d |> group_by(condit,Fit_Method,Best_Model) %>% tally() |> mutate(n=n/6)

d |> group_by(condit,Fit_Method,Best_Model) |> filter(abs(Error_difference)>15) |> tally() |> mutate(n=n/6)

d |> filter(bandInt==100) |> group_by(condit,Fit_Method) |> summarise(m=mean(Error_difference), 
                                              sd=sd(Error_difference), 
                                              n=n(),se=sd/sqrt(n))

# head(map_id,2)
# # A tibble: 2 × 13
# # Groups:   id, condit, Model, Fit_Method [2]
#   id    condit Fit_Method Model          c    lr mean_error  rank nTest nTrain nTotal     n   BIC
#   <fct> <fct>  <chr>      <chr>      <dbl> <dbl>      <dbl> <int> <int>  <int>  <int> <int> <dbl>
# 1 1     Varied Test       ALM   0.00000165  5.32       238.     1    63     86    149    63 -6.80
# 2 1     Varied Test_Train ALM   0.0000634   5.60       276.     1    63     86    149   149 -6.24

```{r fig.width=11, fig.height=12}

#full_comparison |> round_tibble(1) |> reactable(filterable=T,defaultPageSize=15)

@@

d |> filter(abs(Error_difference)>20) |> 
  ggplot(aes(x=vb,y=dist,fill=condit)) + 
  stat_bar + facet_wrap(Fit_Method~Best_Model,ncol=2)
